---
title: "algorithm_comparison"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{algorithm_comparison}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(DoublingBF)
library(parallel)
#p_seq <- c(0.001, 0.01, 0.1, 0.25, 0.4, 0.49, 0.499)
#C_seq <- c(2,5,10,20,50)
C_seq <- c(2, 5, 10, 50, 100, 500, 1000)
eps_seq <- c(0.99, 0.9, 0.75, 0.5, 0.25, 0.1, 0.01, 0.001)
n <- 60000
random_seed <- 1991
num_cores <- 6
max_iter <- list("Nacu_Peres" = 10)
```

# Linear Bernoulli Factory - Algorithm comparison

## Nacu-Peres (for C=2)

Nacu-Peres proposes an algorith that targets $f(p) = \min(2p,1-\epsilon)$. The implementation becomes feasible when paired up with the envelope approach of Latuszynski et al.
The envelopes are given by:
$$
\alpha(k,n) = f(k/n).
$$
$$
\beta(k,n) = f(k/n)+ C_1(p-1/2+3\epsilon)_+\sqrt{2/n} + C_2(p-1/9)_+\exp(-2\epsilon^2n),
$$
where $C_1 = \epsilon^{-1}(1-1/\sqrt{2})^{-1}$, $C_2 = 72(1-\exp(-2\epsilon^2))^{-1}$. For the algorithm to be valid, $\epsilon$ must be smaller than $1/8$, it needs to be initialised with an initial number of tosses $n_0$ to ensure that $\beta(k,n) \in [0,1]$ for all $0\leq k \leq n$. Moreover, these functions are defined only for $n$ begin a power of 2. 

Usually, the algorithm reaches a decision immediately bu just using the initial number of tosses. However, this number can be prohibitive. For instance, if $\epsilon = 1/8$ (the minimum possible for the algorithm to be valid) it requires $32,768$, while if $\epsilon = 0.01$ it requires $n_0 = 268,435,456$:

```{r Nacu_Peres_n0}
eps_seq <- c(0.49,0.4,0.25,0.1,0.01)
res_n0 <- sapply(eps_seq, doubling_find_n0)
```


Nevertheless, the algorithm has a fast simulation in the sense that $\mathbb{P}(N >n) \leq C\rho^n$ - although being often impractible.


## Huber's algorithms comparison
```{r}
# Prepare random seed
set.seed(random_seed, kind="L'Ecuyer-CMRG")
# Set up storing variables
Huber_2019 <- vector("list", length = length(C_seq)*length(eps_seq)) #Save results
df_Huber_2019 <- data.frame(p=numeric(), C=numeric(), eps=numeric(), n=numeric(), est_p=numeric(), est_num_tosses=numeric(), stringsAsFactors = F)
Huber_2017 <- Huber_2019
Huber_2013 <- Huber_2019
df_Huber_2017 <- df_Huber_2019
df_Huber_2013 <- df_Huber_2019
counter <- 1
for(C in C_seq) {
  for(eps in eps_seq){
    # Set the value of p
    p <- (1-eps)/C
    # Huber 2019
    aux <- list_to_matrix(mclapply(1:n, function(iter) {
      doubling_Huber_2019_iter(n=1,C=C,i=1,eps=eps,p=p)
    },mc.cores = num_cores))
    Huber_2019[[counter]] <- list(p=p,C=C,res=aux[1,],num_tosses=aux[2,])
    df_Huber_2019[counter,] <- c(p,C,eps,n,mean(aux[1,]),mean(aux[2,]))
    # Save result
    saveRDS(list(Huber_2013=Huber_2013, Huber_2017=Huber_2017, Huber_2019=Huber_2019, 
                 df_Huber_2013=df_Huber_2013, df_Huber_2017=df_Huber_2017, df_Huber_2019=df_Huber_2019),
            paste0(getwd(),"Huber_comparison_",n,"_",num_cores,"_",random_seed,"_TEMP.rds"))
    # Huber 2017
    aux <- list_to_matrix(mclapply(1:n, function(iter) {
      doubling_Huber_2017(n=1,C=C,eps=eps,p=p)
    },mc.cores = num_cores))
    Huber_2017[[counter]] <- list(p=p,C=C,res=aux[1,],num_tosses=aux[2,])
    df_Huber_2017[counter,] <- c(p,C,eps,n,mean(aux[1,]),mean(aux[2,]))
    saveRDS(list(Huber_2013=Huber_2013, Huber_2017=Huber_2017, Huber_2019=Huber_2019, 
                 df_Huber_2013=df_Huber_2013, df_Huber_2017=df_Huber_2017, df_Huber_2019=df_Huber_2019),
            paste0(getwd(),"Huber_comparison_",n,"_",num_cores,"_",random_seed,"_TEMP.rds"))
    # Huber 2013
    aux <- list_to_matrix(mclapply(1:n, function(iter) {
      doubling_Huber_2014(n=1,C=C,eps=eps,p=p)
    },mc.cores = num_cores))
    Huber_2013[[counter]] <- list(p=p,C=C,res=aux[1,],num_tosses=aux[2,])
    df_Huber_2013[counter,] <- c(p,C,eps,n,mean(aux[1,]),mean(aux[2,]))
    saveRDS(list(Huber_2013=Huber_2013, Huber_2017=Huber_2017, Huber_2019=Huber_2019, 
                 df_Huber_2013=df_Huber_2013, df_Huber_2017=df_Huber_2017, df_Huber_2019=df_Huber_2019),
            paste0(getwd(),"Huber_comparison_",n,"_",num_cores,"_",random_seed,"_TEMP.rds"))
    counter <- counter + 1
  }
}

saveRDS(list(Huber_2013=Huber_2013, Huber_2017=Huber_2017, Huber_2019=Huber_2019, 
                 df_Huber_2013=df_Huber_2013, df_Huber_2017=df_Huber_2017, df_Huber_2019=df_Huber_2019),
            paste0(getwd(),"Huber_comparison_",n,"_",num_cores,"_",random_seed,".rds"))
file.remove(paste0(getwd(),"Huber_comparison_",n,"_",num_cores,"_",random_seed,"_TEMP.rds"))
```

```{r}
# Putting together results from different runs
filenames <- paste0(getwd(),c("Huber_comparison_10000_2_17",
               "Huber_comparison_10000_6_42",
               "Huber_comparison_20000_6_11"),".rds")
# Create function to merge together the lists
merge_res_list <- function(res1,res2) {
  if(length(res1) != length(res2)) {
    stop("The two lists do not share the same length")
  }
  final_res <- vector("list", length=length(res1))
  for(i in 1:length(res1)) {
    l <- list(res1[[i]],res2[[i]])
    keys <- unique(unlist(lapply(l, names)))
    final_res[[i]] <- setNames(do.call(mapply, c(FUN=c, lapply(l, `[`, keys))), keys)
    final_res[[i]]$p <- unique(final_res[[i]]$p)
    final_res[[i]]$C <- unique(final_res[[i]]$C)
  }
  return(final_res)
}
construct_df <- function(l) {
  df <- data.frame(p=numeric(), C=numeric(), eps=numeric(), n=numeric(), mean_p=numeric(), sd_num_tosses=numeric(), mean_num_tosses=numeric(), median_num_tosses=numeric(), stringsAsFactors = F)
  counter <- 1
  for(aux in l) {
    df[counter,] <- c(aux$p,aux$C,1-aux$C*aux$p,length(aux$num_tosses),mean(aux$p),sd(aux$num_tosses),mean(aux$num_tosses),  median(aux$num_tosses))
    counter <- counter+1
  }
  return(df)
}
# Prepare
Huber_2019_all <- vector("list", length=0)
Huber_2017_all <- vector("list", length=0)
Huber_2013_all <- vector("list", length=0)
# Merge results together
for(name in filenames) {
  if(!file.exists(name)) {stop("File name not found")}
  res <- readRDS(name)
  if(length(Huber_2019_all) == 0) {
    Huber_2019_all <- res$Huber_2019
  } else {
    Huber_2019_all <- merge_res_list(Huber_2019_all, res$Huber_2019)
  }
  if(length(Huber_2017_all) == 0) {
    Huber_2017_all <- res$Huber_2017
  } else {
    Huber_2017_all <- merge_res_list(Huber_2017_all, res$Huber_2017)
  }
  if(length(Huber_2013_all) == 0) {
    Huber_2013_all <- res$Huber_2013
  } else {
    Huber_2013_all <- merge_res_list(Huber_2013_all, res$Huber_2013)
  }
}
# Create dataframes
df_Huber_2019_all <- construct_df(Huber_2019_all)
df_Huber_2017_all <- construct_df(Huber_2017_all)
df_Huber_2013_all <- construct_df(Huber_2013_all)
```





